OpenMPIR

### 2017-09-07 paper.tex
Billy to be second author
Small fixes in intro

When writing task-parallel programs today, one has a large selection of
programming models. Unfortunately, despite having significant overlap in
semantics, parallel programming models like OpenMP, Cilk, Kokkos, HPX, Charm++,
Qthreads, pthreads, MPI, Chapel, UPC, etc. have virtually no ability to
interoperate, both at compile time and run time. In addition, many of these
programming models are implemented as libraries, and therefore have no compiler
support. There has been some recent work on specializing compilers to reason
about parallel programming libraries \cite{Moss_2016}, but fragmentation among
models presents a significant challenge for compiler writers, which must choose
a single model to analyze and optimize. An ideal solution would be some form of
common representation of parallelism in an internal representation \textbf{(IR)}.

Compilers use internal representations (IRs) for implementing analyses and
optimizations. Historically, a major drawback for parallel programs is that IRs
haven't had the ability to represent, and therefore reason about, parallelism.
This has prevented the application of common optimizations to concurrent code.
The recent work of Schardl et al. \cite{tapir} has shown that real world
compiler IRs can be extended to represent fork-join parallelism. By extending
the LLVM instruction set with three instructions, they were able to capture all
of the semantics to implement the semantics of Cilk, an extension to C. They
suggested that a similar approach could be taken with OpenMP tasks.

>>>>

When writing task-parallel programs today, one has a large selection of
programming models. Unfortunately, despite having significant overlap in
semantics, parallel programming models like OpenMP, Cilk, Kokkos, HPX, Charm++,
Qthreads, pthreads, MPI, Chapel, UPC, etc. have virtually no ability to
interoperate, both at compile time and run time. In addition, many of these
programming models are implemented as libraries, and therefore have no compiler
support. There has been some recent work on specializing compilers to reason
about parallel programming libraries \cite{Moss_2016}, but fragmentation among
models presents a significant challenge for compiler writers, which must choose
a single model to analyze and optimize. An ideal solution would be some form of
common representation of parallelism.

Compilers use internal representations \textbf{(IRs)} for implementing the
majority of their analyses and optimizations \cite{llvm}. Historically, a major
drawback for parallel programs is that IRs haven't had the ability to
represent, and therefore reason about, parallelism.  This has prevented the
application of common optimizations to concurrent code.  The recent work of
Schardl et al. \cite{tapir} has shown that real world compiler IRs can be
extended to represent fork-join parallelism. By extending the LLVM instruction
set with three instructions, they were able to capture all of the semantics to
implement the semantics of Cilk, an extension to C. They suggested that a
similar approach could be taken with OpenMP tasks.
